Carp\'{e} Data: Supporting Serendipitous Data Integration in Personal Information Management

### 2013-01-10 chi2013-webbox.tex
Figure 1 full width
Remove Table 3 and references to it.

\begin{figure*}[tbp]
\begin{center}
\includegraphics[width=18cm]{img/screenshot}
\caption{DataPalette Workspace, a file manager-inspired Drag and Drop interface for structured data mixing. Collapsible displays of data sources are listed on the left, from which instances or entire sets of items can be dragged to form a window (group) on the workspace.}
\label{fig:workspace}
\end{center}
\end{figure*}

@@

After the studies were complete, we generated transcripts of comments made by participants during the think-aloud protocols. At the same time, we populated a spreadsheet summarising quantitative metrics pertaining to how much various features of the tool were used (see Table \ref{tbl:data} for specific fields).  After the transcriptions were complete, we categorised people's comments made during the study, suggests in their exit survey, and clustered them to common themes.

@@

\newpage
\section{Results}

We received 26 responses to our call, from which we selected the first 20 (ten of whom were female). Seven were non-students, comprised of university staff and alumni; the remainder were students, 8 studying computer science, and 5 studying other subjects.  Due to the large population of international students and staff at our university, we ended up with a large sample (12) of non-native English speakers; however, since all had passed requisite proficiency tests, we did not think this would substantially impact results.  On average, each study took 40 minutes to complete.  The information in Table \ref{tbl:data} summarises the captured metrics for each participant.

\begin{table*}[htbp]
\small
\begin{center}
\begin{tabular}{|r|p{0.3cm}|p{0.3cm}|p{0.3cm}|p{0.3cm}|p{0.3cm}|p{0.3cm}|p{0.3cm}|p{0.3cm}|p{0.3cm}|p{0.3cm}|p{0.3cm}|p{0.3cm}|p{0.3cm}|p{0.3cm}|p{0.3cm}|p{0.3cm}|p{0.3cm}|p{0.3cm}|p{0.3cm}|p{0.3cm}|}
\hline
Participants & 1 &2&3&4&5&6&7&8&9&10&11&12&13&14&15&16&17&18&19&20\\
\hline\hline
gender&f&m&f&f&f&f&f&m&f&f&m&f&m&f&m&m&m&m&m&m\\
A condition first task &y&y&y&n&n&y&n&n&y&y&n&n&y&y&n&n&n&n&n&n\\
\hline\hline
A Condition: task &4&2&3&4&3&&2&1&4&1&4&1&3&2&3&2&1&4&3&2\\
paper used&n&n&n&n&n&n&y&n&y&y&n&y&n&n&y&n&n&n&n&n\\
charts used &1&2&2&0&2&4&5&0&0&0&2&3&2&0&0&0&3&3&4&1\\
maps used &1&1&2&2&2&1&1&0&1&0&1&1&2&1&0&1&0&0&2&1\\ 
same as used &4&3&3&6&0&2&0&2&1&0&6&5&6&2&7&0&6&7&7&7\\
\# data sources used &4&3&4&4&4&3&4&3&4&4&3&3&5&4&5&4&4&5&5&4\\
chosen restaurant/uni &4.1&2.4&3.5&4.3&3.3&&2.4&1.4&4.2&1.6, \newline 1.3, \newline 1.2& 4.2& 1.4, \newline 1.5, \newline 1.3& 3.2& 2.1, \newline 2.3, \newline 2.6& 3.5, \newline 3.3&2.6, \newline 2.3, \newline 2.5&1.6, \newline 1.5, \newline 1.3&4.1&3.3&2.4, \newline 2.5, \newline 2.6\\
\# factors in choice &6&5&4&4&2&4&8&8&6&3&4&8&5&4&7&7&4&5&5&5\\
\hline\hline
 B Condition:task &3&&4&3&4&2&1&2&2&3&2&3&1&4&1&4&2&2&1&3\\
 paper used &n&n&n&n&n&n&y&n&y&y&n&y&n&y&y&n&n&y&n&n\\
% spreadsheet/website&&&&&&&&&&&&&&&&&&&&\\
 number of spreadsheets used&5/5&4/4&2/5&1.5&2/5&5/5&4/4&2/4&3/4&&2/4&4/5&2/4&4/5&2/4&2/5&4/4&4/4&0&5/5\\
 number of websites used&1&1&4&3&3&0&2&3&2&&1&2&3&1&2&3&2&0&4&0\\
 chosen restaurant/uni&3.5&&4.2&3.3&4.3&2.1&1.4, \newline 1.2, \newline 1.6&2.1&2.3, \newline 2.6, \newline 2.5&3.5&2.2, \newline 2.3, \newline 2.6&3.5&1.1&4.1&1.6&4.2&2.6, \newline 2.3, \newline 2.5&2.3, \newline 2.5, \newline 2.6&1.1, \newline 1.3,  \newline 1.4&3.5\\
 \# factors in choice &4&3&2&3&1&6&5&7&7&5&4&7&6&3&6&4&3&6&4&5\\
 \hline
\end{tabular}
\end{center}
\caption{Data collected from each of our trials, for each participant.} \label{tbl:data}
\normalsize
\end{table*}

@@

\subsection{Condition B: Results and Observations}
Participants were given the option of using web sites and/or a spreadsheet to make their choices, using the same data as condition A. There was mixed use of websites and the spreadsheet, and we measured the fraction of the trial time spent in Excel versus looking at the sites in a 5-value range (0,25,50,75,100\%).  Six individuals used Excel entirely (100\%) without consulting the web sites, while one avoided Excel entirely. The uses of Excel for external cognition ranged from collation behaviour to tallying annotations, to colour-coding cells to allow easy identification of  ``pros'' and ``cons''.  The complete data collected is given in Table \ref{tbl:data}. In general, users struggled with both the websites and with the spreadsheet, although could generally find the information they required after a short period of frustration.

>>>>

\begin{figure*}[thb]
\begin{center}
\includegraphics[width=18cm]{img/screenshot}
\caption{DataPalette Workspace, a file manager-inspired Drag and Drop interface for structured data mixing. Collapsible displays of data sources are listed on the left, from which instances or entire sets of items can be dragged to form a window (group) on the workspace.}
\label{fig:workspace}
\end{center}
\end{figure*}

@@

After the studies were complete, we generated transcripts of comments made by participants during the think-aloud protocols. At the same time, we populated a spreadsheet summarising quantitative metrics pertaining to how much various features of the tool were used.  After the transcriptions were complete, we categorised people's comments made during the study, suggests in their exit survey, and clustered them to common themes.

@@

%\newpage
\section{Results}

We received 26 responses to our call, from which we selected the first 20 (ten of whom were female). Seven were non-students, comprised of university staff and alumni; the remainder were students, 8 studying computer science, and 5 studying other subjects.  Due to the large population of international students and staff at our university, we ended up with a large sample (12) of non-native English speakers; however, since all had passed requisite proficiency tests, we did not think this would substantially impact results.  On average, each study took 40 minutes to complete.  %The information in Table \ref{tbl:data} summarises the captured metrics for each participant.

%\begin{table*}[htbp]
%\small
%\begin{center}
%\begin{tabular}{|r|p{0.3cm}|p{0.3cm}|p{0.3cm}|p{0.3cm}|p{0.3cm}|p{0.3cm}|p{0.3cm}|p{0.3cm}|p{0.3cm}|p{0.3cm}|p{0.3cm}|p{0.3cm}|p{0.3cm}|p{0.3cm}|p{0.3cm}|p{0.3cm}|p{0.3cm}|p{0.3cm}|p{0.3cm}|p{0.3cm}|}
%\hline
%Participants & 1 &2&3&4&5&6&7&8&9&10&11&12&13&14&15&16&17&18&19&20\\
%\hline\hline
%gender&f&m&f&f&f&f&f&m&f&f&m&f&m&f&m&m&m&m&m&m\\
%A condition first task &y&y&y&n&n&y&n&n&y&y&n&n&y&y&n&n&n&n&n&n\\
%\hline\hline
%A Condition: task &4&2&3&4&3&&2&1&4&1&4&1&3&2&3&2&1&4&3&2\\
%paper used&n&n&n&n&n&n&y&n&y&y&n&y&n&n&y&n&n&n&n&n\\
%charts used &1&2&2&0&2&4&5&0&0&0&2&3&2&0&0&0&3&3&4&1\\
%maps used &1&1&2&2&2&1&1&0&1&0&1&1&2&1&0&1&0&0&2&1\\ 
%same as used &4&3&3&6&0&2&0&2&1&0&6&5&6&2&7&0&6&7&7&7\\
%\# data sources used &4&3&4&4&4&3&4&3&4&4&3&3&5&4&5&4&4&5&5&4\\
%chosen restaurant/uni &4.1&2.4&3.5&4.3&3.3&&2.4&1.4&4.2&1.6, \newline 1.3, \newline 1.2& 4.2& 1.4, \newline 1.5, \newline 1.3& 3.2& 2.1, \newline 2.3, \newline 2.6& 3.5, \newline 3.3&2.6, \newline 2.3, \newline 2.5&1.6, \newline 1.5, \newline 1.3&4.1&3.3&2.4, \newline 2.5, \newline 2.6\\
%\# factors in choice &6&5&4&4&2&4&8&8&6&3&4&8&5&4&7&7&4&5&5&5\\
%\hline\hline
% B Condition:task &3&&4&3&4&2&1&2&2&3&2&3&1&4&1&4&2&2&1&3\\
% paper used &n&n&n&n&n&n&y&n&y&y&n&y&n&y&y&n&n&y&n&n\\
%% spreadsheet/website&&&&&&&&&&&&&&&&&&&&\\
% number of spreadsheets used&5/5&4/4&2/5&1.5&2/5&5/5&4/4&2/4&3/4&&2/4&4/5&2/4&4/5&2/4&2/5&4/4&4/4&0&5/5\\
% number of websites used&1&1&4&3&3&0&2&3&2&&1&2&3&1&2&3&2&0&4&0\\
% chosen restaurant/uni&3.5&&4.2&3.3&4.3&2.1&1.4, \newline 1.2, \newline 1.6&2.1&2.3, \newline 2.6, \newline 2.5&3.5&2.2, \newline 2.3, \newline 2.6&3.5&1.1&4.1&1.6&4.2&2.6, \newline 2.3, \newline 2.5&2.3, \newline 2.5, \newline 2.6&1.1, \newline 1.3,  \newline 1.4&3.5\\
% \# factors in choice &4&3&2&3&1&6&5&7&7&5&4&7&6&3&6&4&3&6&4&5\\
% \hline
%\end{tabular}
%\end{center}
%\caption{Data collected from each of our trials, for each participant.} \label{tbl:data}
%\normalsize
%\end{table*}

@@

\subsection{Condition B: Results and Observations}
Participants were given the option of using web sites and/or a spreadsheet to make their choices, using the same data as condition A. There was mixed use of websites and the spreadsheet, and we measured the fraction of the trial time spent in Excel versus looking at the sites in a 5-value range (0,25,50,75,100\%).  Six individuals used Excel entirely (100\%) without consulting the web sites, while one avoided Excel entirely. The uses of Excel for external cognition ranged from collation behaviour to tallying annotations, to colour-coding cells to allow easy identification of  ``pros'' and ``cons''. In general, users struggled with both the websites and with the spreadsheet, although could generally find the information they required after a short period of frustration.
